### 2021-11-06 Final Doc/Chapters/Chapter4.tex
Article Proofread

\section{Article}
A literary analysis on the fields of pedagogy, ludology and gamification was conducted and an article written in order to answer the question posed; \textit{What qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information?}
\\\\
This question was then refined and phrased as \textit{What qualities are required for a serious game to be effectively used in an educational environment on various topics?} within the article.
\\\\
The results of the research aspect of this project is the answer to these questions which were synthesised from various case studies and the literature analysis conducted.

>>>>

\section{Article}
A literary analysis on the fields of pedagogy, ludology and gamification was conducted and an article written in order to answer the question posed; \textit{What qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information?} This question was then refined and phrased as \textit{What qualities are required for a serious game to be effectively used in an educational environment on various topics?} within the article.
\\\\
The results of the research aspect of this project is the answer to these questions which were synthesised from various case studies and the literature analysis conducted. The literature study of the article is similar to the one conducted in this document with the addition to an analysis of three case studies in detail, one of which was mentioned in the literature study above in Chapter \ref{Chapter2}.
\\\\
The three case studies made use of are all titled:
\begin{itemize}
\item \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"}
\item \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"}
\item \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"}
\end{itemize}

\noindent Each case study was analysed to determine how the serious games were developed and which principles, qualities or frameworks were a large contributing factor to the development. A summary of the findings from the case studies alone is shown in Table \ref{tab4.1}

\begin{table}[H]
\caption{Design Principles Defined by Case Study (\cite{Dincelli2020,Sheng2007,allers2021children})}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline

\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
\hline
Story-based	& Story-based 			& Simplicity  \\
Reflection	& Reflection			& Clear and Simple Goals  \\
Feedback	& Feedback 				& Quality of Feedback and Rewards  \\
	-		& Conceptual-Procedural	& Structure of the Challenge  \\
	-		& 		-				& Motion-based Interaction  \\
\hline

\end{tabular}
\label{tab4.1}
\end{center}
\end{table}

\noindent
